### 2014-03-01 thesis/src/chapters/chapter-evaluation.tex
Thesis: summary, eval fixes

\section{Introduction}
We carried out a number of tests which aim to prove the solution be better than currently available, especially in terms of:
\begin{enumerate}
  \item deployment cost
  \item cost of providing given Quality-of-Service
  \item deployment time
\end{enumerate}

\subsection*{Hardware and virtual machines configuration}
Many of the carried out tests were run on the same hardware and/or used the same virtual machines so for clarity of presentation their parameters are presented not in a description of every test, but here in table \ref{tab:test-deployment-time-common-hardware-configuration}.

@@

\begin{table}
  \centering
  \begin{tabular}{ | l | l | l | l | }
    \hline                        
    Name & CPU & RAM & HD \\
    \hline
    (virtual machine) carina-frontend  & 1 CPU & 1GB & 6GB \\
    (virtual machine) carina-management-vm  & 1 CPU & 1GB & 9GB \\
    \hline  
  \end{tabular}
  \caption{Configuration of hardware/virtual machines used during tests}
  \label{tab:test-auto-scaling-1cp-hardware-configuration}
\end{table}

@@

\subsubsection{Motivation} This test case aims to prove that scaling across multiple cloud providers is vitally important while ensuring appropriate Quality-of-Service, especially in cases of increased number of service requests. Such scaling scenario, known also as cloud-bursting, leverage benefits arising from offloading application load to an external provider. In order to verify our concept we compare number of transactions per second guaranteed by \emph{Cloud-SAP} and \emph{Carina}. While our proof of concept solution features multi-layer scaling and is cloud federation aware, \emph{Carina} adopts only horizontal scaling. It is expected that test case prove benefits emerging from enriching application platform provider with an cloud federation awareness.

\subsubsection{Scenario}
Testing requires following steps to be done:
\begin{enumerate}
\item deploy exemplary service
\item observe system behaviour under load, simulated by a resource usage mock. It is vital for a resource usage to exceed a single provider capabilities
\item assess system characteristics, including number of handled transactions per second
\end{enumerate}

\subsubsection*{Load simulation}
Similarly to a previous test case, we leveraged a resource mock that allows us to precisely control monitoring information returned to an system. Besides, in order to simplify test case, we were solely focused on a CPU usage. CPU usage function has to exceed upper threshold limit at some point and stay at that level, triggering successive auto-scaling events. However, at some point single cloud provider resources will be surpassed. Equation \eqref{eq:cpu-mock-usage-2cp} denotes a resource usage function that is expected to fulfil above-mentioned scenario and is illustrated in figure \ref{fig:auto-scaling-2cp-cpu-usage-function}.
\begin{equation}
 f(x) = \frac{29}{1500}x^3-\frac{21}{20}x^2+\frac{533}{30}x
 \label{eq:cpu-mock-usage-2cp}
\end{equation}

@@

  \item[\textbf{Deployment diagrams}] Components that took part during testing are show in figures \ref{fig:autoscale-2cp-cloud-sap-deployment-diagram} and \ref{fig:auto-scaling-2cp-carina-deployment-diagram}.

@@

@@

\begin{asparaenum}
  \item[\textbf{Cloud-SAP}] 
   In total, there were 13 vertical (increasing CPU limit) 2 horizontal (adding a container) scaling events. First action took place minute after first violation of scaling policy rule. Since then, slaves' CPU were successively increasing to the point were further scaling wasn't possible - 13th minute of the test. Therefore, \emph{Cloud-SAP} deployed two new slaves on \emph{CP-2}. Listing \ref{lst:auto-scaling-2cp-results-csap-logs} presents logs covering service lifecycle. \lstinputlisting[caption=Cloud-SAP logs excerpt regarding auto-scaling actions on multiple providers, label=lst:auto-scaling-2cp-results-csap-logs]{auto-scaling-2cp-results-csap-logs}

  \item[\textbf{Carina}] 
  Similarly to a \emph{Cloud-SAP}, first scaling event (slave addition) was noticed in 6th minute of test. Scaling jobs were continuously invoked every 2 minutes until capacity of a \emph{CP\-1} hasn been fully exploited. Listing \ref{lst:auto-scaling-2cp-results-carina-jobs} summarises jobs performed by \emph{Carina}. \lstinputlisting[caption=Carina environment manager logs with taken actions (\emph{jobs}), label=lst:auto-scaling-2cp-results-carina-jobs]{auto-scaling-2cp-results-carina-jobs}
\end{asparaenum}

>>>>

\section{Introduction}
We carried out a number of tests which aim to prove the solution to be better than currently available, especially in terms of:
\begin{enumerate}
  \item deployment cost
  \item cost of providing given Quality-of-Service
  \item deployment time
\end{enumerate}

\subsection*{Hardware and virtual machines configuration}
All tests that were carried out were run on the same hardware and/or used the same virtual machines so for clarity of presentation their parameters are presented not in a description of every test, but here in table \ref{tab:test-deployment-time-common-hardware-configuration}.

@@

\begin{table}
  \centering
  \begin{tabular}{  l  l  l  l  }
    \specialrule{.1em}{.05em}{.05em}

    \textbf{Name} & \textbf{CPU} & \textbf{RAM} & \textbf{HD} \\
    \specialrule{.1em}{.05em}{.05em}

    (virtual machine) carina-frontend  & 1 CPU & 1GB & 6GB \\ \hline
    (virtual machine) carina-management-vm  & 1 CPU & 1GB & 9GB \\
    \hline  
  \end{tabular}
  \caption{Configuration of hardware/virtual machines used during tests}
  \label{tab:test-auto-scaling-1cp-hardware-configuration}
\end{table}

@@

\subsubsection{Motivation} This test case aims to prove that scaling across multiple cloud providers is vitally important when ensuring appropriate Quality-of-Service, especially in cases of increased number of service requests. Such scaling scenario, known also as cloud-bursting, leverage benefits arising from offloading application load to an external provider. In order to verify our concept we compare number of transactions per second guaranteed by \emph{Cloud-SAP} and \emph{Carina}. While our proof of concept solution features multi-layer scaling and is cloud federation aware, \emph{Carina} adopts only horizontal scaling. It is expected that test case prove benefits emerging from enriching application platform provider with a cloud federation awareness.

\subsubsection{Scenario}
Testing requires following steps to be done:
\begin{enumerate}
\item deploy an exemplary service
\item observe system behaviour under load, simulated by a resource usage mock. It is vital for a resource usage to exceed a single provider capabilities
\item assess system characteristics, including number of handled transactions per second
\end{enumerate}

\subsubsection*{Load simulation}
Similarly to a previous test case, we leveraged a resource mock that allows us to precisely control monitoring information returned to an system. Besides, in order to simplify test case, we were solely focused on a CPU usage. CPU usage function has to exceed upper threshold limit at some point and stay at that level, triggering successive auto-scaling events. However, at some point single cloud provider resources will be surpassed. Equation \eqref{eq:cpu-mock-usage-2cp} denotes a resource usage function that is expected to fulfil above-mentioned conditions and is illustrated in figure \ref{fig:auto-scaling-2cp-cpu-usage-function}.
\begin{equation}
 f(x) = \frac{29}{1500}x^3-\frac{21}{20}x^2+\frac{533}{30}x
 \label{eq:cpu-mock-usage-2cp}
\end{equation}

@@

  \item[\textbf{Deployment diagrams}] Components that took part during test are show in figures \ref{fig:autoscale-2cp-cloud-sap-deployment-diagram} and \ref{fig:auto-scaling-2cp-carina-deployment-diagram}.

@@

\subsubsection*{Test case duration}
The test case lasts 25 minutes.

@@

\begin{asparaenum}
  \item[\textbf{Cloud-SAP}] 
   In total, there were 13 vertical and 2 horizontal scaling events. First action took place minute after first violation of scaling policy rule. Since then, slaves' CPU were successively increasing to the point were further scaling wasn't possible - 13th minute of the test. Therefore, \emph{Cloud-SAP} deployed two new slaves on \emph{CP-2}. Listing \ref{lst:auto-scaling-2cp-results-csap-logs} presents logs covering service lifecycle. \lstinputlisting[caption=Cloud-SAP logs excerpt regarding auto-scaling actions on multiple providers, label=lst:auto-scaling-2cp-results-csap-logs]{auto-scaling-2cp-results-csap-logs}

  \item[\textbf{Carina}] 
  Similarly to a \emph{Cloud-SAP}, first scaling event (slave addition) was noticed in 6th minute of test. Scaling jobs were continuously invoked every 2 minutes until capacity of a \emph{CP\-1} has not been fully exploited. Listing \ref{lst:auto-scaling-2cp-results-carina-jobs} summarises jobs performed by \emph{Carina}. \lstinputlisting[caption=Carina environment manager logs with taken actions (\emph{jobs}), label=lst:auto-scaling-2cp-results-carina-jobs]{auto-scaling-2cp-results-carina-jobs}
\end{asparaenum}

### 2014-03-01 thesis/src/chapters/chapter-summary.tex
Thesis: summary, eval fixes

\chapterintro{This chapter provides the summery of the dissertation and gives information about future work and research directions.}

\section{Conclusions}
In this dissertation we proposed an architecture of a platform that ensures satisfying Quality of Service requirements of users' applications deployed in a cloud computing environment. The key attribute of the proposed system is holistic approach to self-adaptability achieved by insightful understanding of platform-as-a-service model. As a consequence, designed architecture manages variety of resources that users' applications incorporate leading to a system that is capable of vertical, horizontal and most importantly cloud-federation aware scaling. Additionally, we implemented a minimal viable product which conforms to the devised architecture and made its evaluation by performing tests which compare it to some of the currently available solutions.

@@

All tests of the platform were not simulated on any software, but conducted on the real hardware forming a home-made data center. Tests were chosen and design so as to reflect at the highest possible rate real business use cases. Their results show considerable potential of the proposed solution. Nevertheless, we did not manage to evaluate implementation in a real-world scenario that entails using enterprise-level application such as the ones based on Java Enterprise Edition.

>>>>

\chapterintro{This chapter provides the summary of the dissertation and gives information about future work and research directions.}

\section{Conclusions}
In this dissertation we proposed an architecture of a platform that ensures satisfying Quality of Service requirements of users' applications deployed in a cloud computing environment. The key attribute of the proposed system is holistic approach to a self-adaptability achieved by an insightful understanding of a platform-as-a-service model. As a consequence, designed architecture manages variety of resources that users' applications incorporate leading to a system that is capable of vertical, horizontal and most importantly cloud-federation aware scaling. Additionally, we implemented a minimal viable product which conforms to the devised architecture and made its evaluation by performing tests which compare it to some of the currently available solutions.

@@

All tests of the platform were not simulated on any software, but conducted on the real hardware forming a home-made data center. Tests were chosen so as to reflect at the highest possible rate real business use cases. Their results show considerable potential of the proposed solution. Nevertheless, we did not manage to evaluate implementation in a real-world scenario that entails using enterprise-level application such as the ones based on Java Enterprise Edition.
